%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \expentry
    {Member Technical Staff} % Job title
    {NetApp} {India Pvt. Ltd.} % Organization
    {A Fortune 500 Hybrid Cloud Data Management Solutions Company} % Organization Description
    {Dec. 2018 - Present} % Date(s)
    {Bangalore, India} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Pioneered the design and implementation of core space management functionalities for OntapX, NetApp's
		next-generation disaggregated data management platform. This included contributing to the development
		of automatic space rebalancing, space reservation management ensuring guaranteed client operations,
		and proactive space reclamation mechanisms leveraging automated snapshot deletion.}
        \item {Led the complete development lifecycle for Granular Data Distribution on NAS volumes, conceiving and
		architecting novel solutions for efficient space guarantee management, automated healing processes, and
		robust lost data recovery strategies for distributed files (patent pending).}
	\item {Spearheaded the design and implementation of the multipart file layout export to pNFS clients, enhancing
		interoperability and performance.}
	\item {Led a critical initiative to replace fixed space reservation for the inode metafile with a dynamic
		allocation strategy, resulting in a 50\% reduction in reserved volume metadata space and an 8x increase in
		the maximum file capacity per volume.}
        \item {Devised the optimization of the cluster-level space attribute reporting infrastructure by implementing a
		strategic caching mechanism. This resulted in a significant performance improvement, reducing REST API
		response times from over 5 seconds to under 1 second.}
	\item {Drove the containerization of core Ontap data management components, a foundational effort for NetApp's
		software-defined cloud storage solution, which evolved into the core of Google Cloud NetApp Volumes.
		Oversaw the implementation of critical system startup, software upgrade, and liveness/readiness probes for
		Data Management pods, proactively identifying numerous issues early in the development cycle.}
        \item {Engineered and implemented a critical memory protection scheme within the Data Management binary to safeguard
		system-critical memory pages from unintended modifications, demonstrating a deep understanding of system
		reliability and stability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \expentry
    {Staff Software Development Engineer} % Job title
    {Infinera} {India Pvt. Ltd.} % Organization
    {A Global Supplier of Innovative Networking Solutions; A Pioneer in Large-Scale Photonic Integrated Circuits Design} % Organization Description
    {Jul. 2012 - Nov. 2018} % Date(s)
    {Bangalore, India} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Ideated a significant enhancement to the Network Element Transaction Framework by introducing a private
	      workspace for write transactions, enabling support for 15 simultaneous NMS connections on a 64-chassis
	      Network Element cluster, over the previous limitation of 3 connections.}
      \item {Conceptualized and delivered a novel Network Element Link Traversal Framework to streamline fault correlation
	      logic (later patented). This framework's adoption across multiple features led to a remarkable reduction in
	      traversal-related bugs from an average of 2 per feature to zero.}
      \item {Architected and developed a declarative Fault Correlation and Management Framework for the Software
	      Defined Network suite. This innovative framework enabled the dynamic specification of new alarm
	      definitions and fault correlation rules without requiring recompilation (patent filed.)}
      \item {Engineered and implemented a reusable C++ Cryptographic Wrapper Library enabling digital signature
	      verification and decryption for Instant Bandwidth licenses. This library's subsequent
	      adoption across several other security features highlights its robust design and broad applicability.}
      \item {Contributed significantly to the full software development lifecycle – from object modeling to implementation
	      and delivery – of numerous Network Element Management Plane Software modules. This included Optical
	      Amplifiers, Broadcasting Modules, Multiplexers, Cross-Connects, and Protection Switching modules,
	      demonstrating a comprehensive understanding of network element functionality across multiple releases.
	      }
      \end{cvitems}
    }

%---------------------------------------------------------
  \expentry
    {Lead Engineer, R\&D} % Job title
    {Tejas Networks} {Ltd.} % Organization
    {A TL 9000 Certified Optical Networking Products Company} % Organization Description
    {Jun. 2006 - Jun. 2012} % Date(s)
    {Bangalore, India} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a performance optimization initiative for Network Element Software transactions by implementing
		backgrounding and batching of configuration database commits. This critical enhancement resulted in
		a significant reduction in centralized NMS-based circuit restoration timings from 40 seconds to sub-second,
		and earned an achievement award.}
        \item {Architected and implemented diverse Automatically Switched Optical Network (ASON) service classes
		leveraging Generalized Multi-Protocol Label Switching (GMPLS). Additionally, designed and developed
		a User Mode Linux-based simulation framework, which drastically reduced unit-testing time, showcasing
		a focus on development efficiency.}
	\item {Designed and developed a robust System Startup and Failover Manager featuring a state machine-based
		phased initialization of Network Element Software, demonstrating strong system design skills.}
	\item {Spearheaded efforts to improve the management layer security of Network Elements by implementing HTTPS
		support for the web server, robust user session management, and comprehensive audit logging of configuration
		changes. This initiative significantly enhanced the security posture of the network elements.}
	\item {Streamlined user management across multiple Network Elements by designing and implementing support for
		centralized RADIUS-based authentication. This key feature relieved operators from the cumbersome task of
		managing users individually on each network element, improving operational efficiency.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
