%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Honors \& Awards}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
% \cvsubsection{International}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\begin{cventries}

  \honorentry
    {NetApp} % Presenter
    {Spot Bonus Reward} % Award
    {Bangalore, India}
    {
	\honorsubentry
	  {Awarded for stepping in during absence of the lead designer to deliver last-minute design changes for the TCM project.}
	  {Apr. 2023}
	\honorsubentry
	  {Recognized for driving to the development of Automatic Incremental Repair for the Flex Group Rebalancing project.}
	  {Jul. 2022}
	\honorsubentry
	  {Rewarded for contributions to the Flex Group Rebalancing project and mentoring new joiners.}
	  {Jan. 2022}
    }

%-------------------------------------------------------------------------------
  \honorentry
    {NetApp Hackathon} % Presenter
    {Hackathon Notable Project Winner} % Award
    {Bangalore, India}
    {
	\honorsubentry
	  {Awarded for demonstrating of the idea of ``Photon Asynchronous IO Using io\_uring.''}
	  {Nov. 2022} % Date(s)
	\honorsubentry
	  {Awarded for demonstratimg the idea of ``Vertical Pod Autoscaling for DMAP Containers.''}
	  {Feb. 2020} % Date(s)
    }

%-------------------------------------------------------------------------------
  \honorentry
    {NetApp} % Presenter
    {Peer Recognition Award} % Award
    {Bangalore, India}
    {
	\honorsubentry
	  {Recognized for teamwork during the ``Quark Version Upgrade'' project by the Cloud Engineering Team Peers.} % Description
	  {May. 2020} % Date(s)
    }

%-------------------------------------------------------------------------------
  \honorentry
    {Infinera} % Presenter
    {Spot Bonus Reward} % Award
    {Bangalore, India}
    {
	\honorsubentry
	  {Rewarded for significant contributions to design and development of FBM Management Plane Software.}
	  {Mar. 2017} % Date(s)
	\honorsubentry
	  {Rewarded for exceptional performance in design and development of Fault Integration and Alarm Correlation.} % Description
	  {Jun 2015} % Date(s)
    }

%-------------------------------------------------------------------------------
  \honorentry
    {Infinera Hackathon} % Presenter
    {Hackathon Star Project Award} % Award
    {Bangalore, India}
    {
	\honorsubentry
	  {Awarded for demonstrating the project titled ``Parametric Software.''} % Description
	  {Jun. 2015} % Date(s)
    }

%-------------------------------------------------------------------------------
  \honorentry
    {Tejas Networks} % Presenter
    {Achievement Award} % Award
    {Bangalore, India}
    {
	\honorsubentry
	  {Awarded for optimizations in management plane software to reduce ASON circuit restoration time.} % Description
	  {Apr. 2011} % Date(s)
    }

%-------------------------------------------------------------------------------
  \honorentry
    {Mukti, An Annual National Level Technical Symposium, Linux Users' Group, NIT} % Presenter
    {Overnight Contest Winner} % Award
    {Durgapur, India}
    {
	\honorsubentry
	  {First Prize in C Programming Contest.}
	  {Jan. 2006} % Date(s)
	\honorsubentry
	  {Third Prize in System Admininstration Contest.}
	  {Jan. 2006} % Date(s)
    }

%-------------------------------------------------------------------------------

\end{cventries}


